NEW TITLE

### 2019-10-21 paper.tex
Preparing for submission to TandF journal

\documentclass{article}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{todonotes}

@@

@@

\section{Acknowledgements}

@@

\bibliographystyle{plain}
\bibliography{bib}

>>>>

\documentclass[]{interact}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[natbibapa,nodoi]{apacite}

\setlength\bibhang{12pt}
\renewcommand\bibliographytypesize{\fontsize{10}{12}\selectfont}

@@

\articletype{Review Draft}

\title{NEW TITLE}

\author{%
  \name{Jacobus C. Lock\textsuperscript{a}\thanks{Contact Author}, Iain D. Gilchirst\textsuperscript{b}, Grzegorz Cielniak\textsuperscript{a} and Nicola Bellotto\textsuperscript{a}}%
  \affil{\textsuperscript{a}University of Lincoln, Lincoln, LN6 7TS, UK; \textsuperscript{b}University of Bristol, Bristol, BS8 1TH, UK}%
}

\maketitle

\begin{abstract}
  Cool and informative abstract
\end{abstract}

\begin{keywords}
  Visual impairment; active vision; guidance system; audio interface; Fitts Law
\end{keywords}

@@

\section*{Acknowledgements}

@@

\bibliographystyle{apacite}
\bibliography{bib}
